A Parallel, Backjumping Subgraph Isomorphism Algorithm using Supplemental Graphs

### 2015-06-20 paper/paper.tex
Lazy fold

        (In effect we are treating the $\KwSty{foreach}$ loop as a parallel fold, so that a subtree
        does not depend upon items to its left. Backjumping conditions are left-zero elements
        \cite{Lobachev:2012}, although we do not have a unique zero.)

>>>>

        (In effect we are treating the $\KwSty{foreach}$ loop as a parallel lazy fold, so that a
        subtree does not depend upon items to its left. Backjumping conditions are left-zero
        elements \cite{Lobachev:2012}, although we do not have a unique zero.)
